Distinction Centrality Analysis

### 2025-07-30 analysis.qmd
new ex who dis

```{r Toy Examples}
   g1 <- make_star(7, mode = "undirected") # star graph
   g2 <- g1 + edge(2,3)
   g2 <- g2 + edge(2,4)
   g2 <- g2 + edge(3,4)
   g2 <- g2 + edge(5,6)
   g2 <- g2 + edge(5,7)
   g2 <- g2 + edge(6,7) # structural fold
   g3 <- g1 + edge(2,4)
   g3 <- g3 + edge(3,4)
   g3 <- g3 + edge(5,6)
   g3 <- g3 + edge(5,7) # intra-connected clusters
   g4 <- g3 + edge(2,7) # inter-connected clusters
   g5 <- make_ring(7) #circle graph
   g6 <- g5 + edge(6,1) # circle graph plus triangle
   g7 <- g5 + edge(7,4) # circle graph plus long tie
   g8 <- make_full_graph(7, directed = FALSE) # clique
   g9 <- make_full_graph(6, directed = FALSE)
   g9 <- add_vertices(g9, 1)
   g9 <- g9 + edge(1,7) # kite
   g10 <- g1 + edge(2,3)
   g10 <- g10 + edge(3,4)
   g10 <- g10 + edge(4,5)
   g10 <- g10 + edge(5,6)
   g10 <- g10 + edge(6,7)
   g10 <- g10 + edge(7,2) #wheel graph
   g11 <- make_ring(8) #circle graph
   g11 <- delete_vertices(g11, 8) #path graph
```

>>>>

```{r Toy Examples}
   g1 <- make_star(7, mode = "undirected") # star graph
   g2 <- g1 + edge(2,3)
   g2 <- g2 + edge(2,4)
   g2 <- g2 + edge(3,4)
   g2 <- g2 + edge(5,6)
   g2 <- g2 + edge(5,7)
   g2 <- g2 + edge(6,7) # structural fold
   g3 <- g1 + edge(2,4)
   g3 <- g3 + edge(3,4)
   g3 <- g3 + edge(5,6)
   g3 <- g3 + edge(5,7) # intra-connected clusters
   g4 <- g3 + edge(2,7) # inter-connected clusters
   g5 <- make_ring(7) #circle graph
   g6 <- g5 + edge(6,1) # circle graph plus triangle
   g7 <- g5 + edge(7,4) # circle graph plus long tie
   g8 <- make_full_graph(7, directed = FALSE) # clique
   g9 <- make_full_graph(6, directed = FALSE)
   g9 <- add_vertices(g9, 1)
   g9 <- g9 + edge(1,7) # kite
   g10 <- g1 + edge(2,3)
   g10 <- g10 + edge(3,4)
   g10 <- g10 + edge(4,5)
   g10 <- g10 + edge(5,6)
   g10 <- g10 + edge(6,7)
   g10 <- g10 + edge(7,2) #wheel graph
   g11 <- make_ring(8) #circle graph
   g12 <- delete_vertices(g11, 8) #path graph
```

```{r Bonacich examples}
   g13 <- make_empty_graph(10, directed = FALSE)
   g13 <- g13 + edge(1,2)
   g13 <- g13 + edge(1,3)
   g13 <- g13 + edge(1,9)
   g13 <- g13 + edge(2,3)
   g13 <- g13 + edge(2,10)
   g13 <- g13 + edge(3,4)
   g13 <- g13 + edge(4,5)
   g13 <- g13 + edge(4,6)
   g13 <- g13 + edge(5,10)
   g13 <- g13 + edge(5,6)
   g13 <- g13 + edge(6,7)
   g13 <- g13 + edge(7,8)
   g13 <- g13 + edge(7,9)
   g13 <- g13 + edge(8,10)
   g13 <- g13 + edge(8,9) #Bonacich (2007) regular network Fig. 5
   g14 <- make_empty_graph(12, directed = FALSE)
   g14 <- g14 + edge(1,2)
   g14 <- g14 + edge(1,6)
   g14 <- g14 + edge(1,7)
   g14 <- g14 + edge(2,3)
   g14 <- g14 + edge(2,10)
   g14 <- g14 + edge(3,4)
   g14 <- g14 + edge(3,8)
   g14 <- g14 + edge(4,5)
   g14 <- g14 + edge(4,11)
   g14 <- g14 + edge(5,6)
   g14 <- g14 + edge(5,9)
   g14 <- g14 + edge(6,12)
   g14 <- g14 + edge(7,8)
   g14 <- g14 + edge(7,9)
   g14 <- g14 + edge(8,9)
   g14 <- g14 + edge(10,11)
   g14 <- g14 + edge(10,12)
   g14 <- g14 + edge(11,12)
   plot(g14)
```

```{r Estrada examples}
   g15 <- make_empty_graph(8, directed = FALSE)
   g15 <- g15 + edge(1,2)
   g15 <- g15 + edge(1,5)
   g15 <- g15 + edge(1,8)
   g15 <- g15 + edge(2,3)
   g15 <- g15 + edge(2,8)
   g15 <- g15 + edge(3,4)
   g15 <- g15 + edge(3,6)
   g15 <- g15 + edge(4,5)
   g15 <- g15 + edge(4,7)
   g15 <- g15 + edge(5,6)
   g15 <- g15 + edge(6,7)
   g15 <- g15 + edge(7,8) #Fig 1(a) https://doi.org/10.1103/PhysRevE.71.056103
   distinction(g15, norm = TRUE)
```

```{r}
   n <- 5
   g9 <- make_full_graph(n, directed = FALSE)
   g9 <- add_vertices(g9, 1)
   g9 <- g9 + edge(n, n+1) # kite
   distinction(g9, norm = FALSE)
```
